Defining properties regulating pioneer-factor binding and function

### 2023-03-01 manuscript/manuscript_sections/_06_Figure_Legends.qmd
update supp figures

**Extended Data Figure 10: Expression of Zld and Grh DNA-binding domains at protein levels comparable to the full-length proteins. a-b,** Immunoblots showing titration of protein levels for Zld (a) or Grh (b) DNA-binding domains to match expression of the full-length proteins. DNA-binding domain protein levels are shown at a range of CuSO~4~ concentrations and compared to an equivalent number of cells expressing full-length Zld or Grh at approximately physiological levels. **c,** Metaplots showing the average ChIP-seq signal for full-length Zld or the DNA-binding domain alone at the subset of previously identified class I, II or III binding sites that contain a canonical Zelda CAGGTAG motif.

>>>>

**Extended Data Figure 10: Expression of Zld and Grh DNA-binding domains at protein levels comparable to the full-length proteins. a-b,** Immunoblots showing titration of protein levels for Zld (a) or Grh (b) DNA-binding domains to match expression of the full-length proteins.
DNA-binding domain protein levels are shown at a range of CuSO~4~ concentrations and compared to an equivalent number of cells expressing full-length Zld or Grh at approximately physiological levels.
**c-d,** Immunofluorescent microscopy images of stable cell lines expressing full-length protein or DBD only for Zld (c) or (Grh).
Stable cell lines are compared to WT cells.
**e,** Metaplots showing the average ChIP-seq signal for full-length Zld or the DNA-binding domain alone at the subset of previously identified class I, II or III binding sites that contain a canonical Zelda CAGGTAG motif.
